\chapter{Introduction}\label{chap:introduction}

{\color{purple} {\color{blue} Ajay} and {\color{black} Vijay} went to the same highschool over a decade ago. After going to different universities and working in different cities, they decide to catch up on some unremarkable day. They meet at a pub. Aged 30-something, they talk about how life has been, about career choices, and future plans. {\color{blue}Ajay} has worked for some finance firm or another, working with accounting, business planning, and so on... {\color{black} Vijay} has been jumping to and fro between IT roles and engineering jobs.

A few beers in...}

{\color{blue} Ajay: Life really hasn't been what I hoped it would be. I have decided to do something else. I have a decent bit of cash saved up to work on this new project.} 

Vijay: I told you already, dog-whisperer sounds fun, but it's not going to take off. 

{\color{blue} Ajay: Not that one, although I insist dog-whisperer is going to be a mainstream profession any day now. Enough about that. I'm talking about investing in sports.}

Vijay: You mean like those competitions where dogs jump through hoops and run through tunnels? 

{\color{blue} Ajay: No. Not that one either. Nothing about dogs. I'm serious. I want to invest in sports. I want to see more people playing more sports. Remember back when we used to play cricket on the streets? Or fought with other groups of kids for a spot on a ground?}

Vijay: Oh yeah. I remember that. I also remember that one time when you guys egged me on to confront that senior from school, but ran away like headless chickens when he started punching me. I ran up a fever after that and had to stay in bed for 2 days, and you guys ...

{\color{blue} Ajay: Let's not worry about what happened over ten years ago. My point is, the sports infrastructure in the city was shiet. It's worse now, because all of those empty spots we claimed for cricket are gone, used up for construction of some residence or business or something else. There's too many cars parked on the streets, so kids today can't even play on the streets like we used to.}

Vijay: They could play at school...

{\color{blue} Ajay: Really? At school? Did you forget where we went to school?}

Ahem... You must admit that playing cricket on the rooftop and running down three floors of stairs to bring back a ball had a certain appeal to it. 

{\color{blue} Yeah, right. My point is, most schools don't have playground. There are no decent parks. Even if there are, the parks are off limits for kids to play at. All of the vacant grounds are being used up. Streets have too much traffic and parked cars. There's really no place for kids to play at. And forget about adults. When was the last time you played something?}

Last week I think

{\color{blue} Computer games don't count!}

Alright. Fine. I see your point. There are very few sports facilities. I think I can see where you are going. You want to build a sports facility, right? It is going to be quite expensive. Just the cost of leasing the land will be very high, what with the real estate boom in the city? And installing a surface? Do we even have any of that in the city? Maintenance? Forget about it.The facility is going to be in tatters within a month. Look at brand new airports and railways in the country. A few months and they're garbage. And that is in spite of having armies of personnel to look after them. Can you afford any of that?

{\color{blue} Sigh... If there is a nice indoor volleyball court in the street next to yours, and you can play there everyday for the cost that's twice a gym membership, would you go play?}

Of course. But that's just wishful thinking. There aren't any volleyball courts like that. 

{\color{blue} There are. Quite a few of them actually. You can book a court for an hour for about a thousand rupees. Split that among 10 players, and that's a hundred bucks. Play 3 days a week, that costs you 1,200 rupees a month. How does that sound?}

No way! Why haven't I heard of this before. Where is this sports hall you're talking about. If there really is one nearby, I'd definitely go. 

{\color{blue} That's the problem. There aren't many of them. At least not for volleyball. There are a lot more indoor sports halls for badminton. They usually charge about INR 400 per hour per court. They are well maintained. Don't expect air-conditioned halls, but expect clean courts and reasonable ventilation. There are a few apps going around that help you book these courts or find players to team up with.}

Problem solved then, isn't it. So, do you want to invest in publicizing these facilities?

{\color{blue} No. There are far too few of these facilities. Nowhere near enough to cover all of the sports enthusiasts in the city. I want to build more of these facilities. Starting with just the one. Hopefully, over a few decades, I can expand to cover the entire city. We can have lots of coaching camps, seasonal tournaments, scholarships, live telecasting. We can make proper sports leagues out of all this. In a nation that is dominated by cricket, I believe we can make a real difference if we can build sports infrastructure at this grassroots level. We can then move to other cities in the state, maybe the country.}

Okay. Time out. Two things. First, you seem to know what you're talking about. I'm impressed, and that's not just the beer talking. Second, who is this "we"? While I'm happy to patronize your sports facilities, if you ever get them running, I'm far too poor to be investing on this scale. 

{\color{blue} I have a few other people interested. I haven't spent the past decade working with businesses for nothing. I've schmoozed my way through a lot of people interested in sports infrastructure. In fact, we are halfway through putting together a proposal to get some venture capital. We have the business plan and the initial capital. The issue we're working on right now is location. I'd love to set up our first facility close to where I live, but I don't know if that's a good idea. We've been arguing over this for a week now, and still couldn't agree on a location.}

Hmmm... Location indeed. That is an interesting question. In fact, let me google a few things. 

You're right. There are quite a few existing sports facilities. They're not all businesses though. Quite a few belong to colleges and governmental organizations. In any case, it shouldn't be hard to use these locations to train a model and extract a few candidate locations. 

{\color{blue} Train a model. Why are we getting into using models. Beautiful young ladies do have that charm that can help a business case, but that's really not something I'm keen on.}

<Facepalm> That is not what I mean. I'm not talking about models that show up in advertisements and fashion shows. I mean machine learning, artificial intelligence. Are you sure you have worked with businesses for the better part of ten years?

{\color{blue} Ah! Hahaha. I see. Don't look at me like I'm an idiot. There isn't much of that kind of modelling going on in the businesses I work with. I see your point. I'm not good at that stuff though. In fact, I know next to nothing, and neither do any of my partners.}

I kind of figured that when you thought of supermodels. I might be able to help. It just so happens that I have recently been dabbling in data science and machine learning. I'm looking for a pet project to build some proper experience. This could be just the thing I'm looking for. 

{\color{blue} Really? You can help me do this? That would really help me out. But are you sure you can do it, considering your inexperience. What if you get it wrong? I might lose a lot of money, you know.}

Whoa! Cool it. I'm offering to do it for no pay, and you're already ready to pile it on me? If that's how it's going to be, then I'm not doing it. You can find your own way to figure out the best location, and convince your partners and your investors for its suitability. 

{\color{blue} You know what? That just might do the trick. You will train this model thing. And we can then tweak it a little bit to get it to work for me. I can then show it to my investors. They won't argue with me when they see all of the fancy maths.}

Nope. Not a chance. I will help you, but I'll not do your dirty work. Tell you what. I'll do the modelling bit. I explain how all of it works. You can then take it, learn what you can, and tinker with it to see if it helps your case. 

{\color{blue} Hmmm... Okay. That sounds fair.}

I'm not done yet. Whenever we meet to talk about the work I'm doing for you, we'll meet at a fancy pub. And you foot the bill. Deal?

{\color{blue} Deal.}
